LSOA domestic Electricty and Gas maps

### 2021-08-24 LSOA domestic Elec and Gas.Rmd
Trying to fix the error in mapping the difference in electricty consumpton map

# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference between 2010 and 2019 dom elec
```{r Creating the difference in LSOA mean dom elec consumption variable}
domelec_LSOA_2010 <- readr::read_csv(paste0(dataFolder,"energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2010.csv"))
domelec_LSOA_2019 <- readr::read_csv(paste0(dataFolder, "energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2019.csv"))
domelec_LSOA_2010$de2010 <- domelec_LSOA_2010$'Mean domestic electricity consumption \n(kWh per meter)'
domelec_LSOA_2019$de2019 <- domelec_LSOA_2019$'Mean domestic electricity consumption \n(kWh per meter)'
# create unambiguos lsoa code for matching to each other and the sf geometry
domelec_LSOA_2010$LSOA11CD <- domelec_LSOA_2010$`Lower Layer Super Output Area (LSOA) Code`
domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`

merged_de <- merge(domelec_LSOA_2010, domelec_LSOA_2019, by="LSOA11CD", all=TRUE)
names(merged_de)
merged_de$de_diff<-as.numeric(merged_de$de2019)-as.numeric(merged_de$de2010) ##Fixed
summary(merged_de)
```

```{r Mapping the LSOA difference in mean dom elec consumption}
# merge to sf geometry on LSOA11CD
lsoa_sf_de20102019<-merge(lsoa_sf_data, merged_de)
ggplot2::ggplot(lsoa_sf_de20102019, aes(fill=de_diff))+
                  geom_sf() +
                  scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red") +
  labs(caption="Solent(all LSOAs)")

@@

#####Cities in more detail
```{r Southampton LSOA difference in dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LSOA11CD == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Southampton")
#BROKEN
```
```{r Portsmouth LSOA difference in dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LSOA11CD == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de-diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA difference in dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Winchester")
# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Winchester")
```

>>>>

# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference between 2010 and 2019 dom elec
```{r Creating the difference in LSOA mean dom elec consumption variable}
domelec_LSOA_2010 <- readr::read_csv(paste0(dataFolder,"energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2010.csv"))
domelec_LSOA_2019 <- readr::read_csv(paste0(dataFolder, "energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2019.csv"))
domelec_LSOA_2010$de2010 <- domelec_LSOA_2010$'Mean domestic electricity consumption \n(kWh per meter)'
domelec_LSOA_2019$de2019 <- domelec_LSOA_2019$'Mean domestic electricity consumption \n(kWh per meter)'
# create unambiguous lsoa code for matching to each other and the sf geometry
domelec_LSOA_2010$LSOA11CD <- domelec_LSOA_2010$`Lower Layer Super Output Area (LSOA) Code`
domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`

merged_de <- merge(domelec_LSOA_2010, domelec_LSOA_2019, by="Lower Layer Super Output Area (LSOA) Code", all=TRUE)
names(merged_de)
merged_de$de_diff<-as.numeric(merged_de$de2019)-as.numeric(merged_de$de2010) 
summary(merged_de)
```

```{r Mapping the LSOA difference in mean dom elec consumption}
# merge to sf geometry on LSOA11CD
merged_de$LSOA11CD <- merged_de$"Lower Layer Super Output Area (LSOA) Code"
lsoa_sf_de20102019<-merge(lsoa_sf_data, merged_de)
ggplot2::ggplot(lsoa_sf_de20102019) + geom_sf(aes(fill=de_diff))+
                  scale_fill_continuous(name="Change in Mean consumpton (kWh per meter)",low="green",high="red") +
  labs(caption="Solent(all LSOAs)")

@@

#####Cities in more detail
```{r Southampton LSOA difference in dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_sf_de20102019, LSOA11NM == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill= de_diff)) +
  scale_fill_continuous(name = "Change in Mean consumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Southampton")
#BROKEN
```
```{r Portsmouth LSOA difference in dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LSOA11CD == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de-diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA difference in dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Winchester")
# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
